Spatial and Temporal Analysis of Bicycle Thefts in Toronto

### 2024-11-08 paper/A2-starter-code.Rmd
charts updated

```{r}
# Create a pie chart for the status of bicycle thefts
bike_thefts %>%
  count(STATUS) %>%
  ggplot(aes(x = "", y = n, fill = STATUS)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(title = "Bicycle Theft Status (Stolen vs Recovered)") +
  theme_minimal()

# Save the plot
# ggsave(here("other/charts/theft_status_pie.png"))
```

```{r}
# Create a bar chart for bicycle thefts by day of the week
bike_thefts %>%
  count(OCC_DOW) %>%
  ggplot(aes(x = reorder(OCC_DOW, -n), y = n, fill = OCC_DOW)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Bicycle Thefts by Day of the Week", x = "Day of the Week", y = "Number of Thefts") +
  theme_minimal()

# Save the plot
# ggsave(here("other/charts/thefts_by_day.png"))
```

@@

# Plot the map with bike theft locations data
ggplot() +
  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
  geom_point(
    data = coordinates_data, aes(x = longitude, y = latitude),
    size = 0.5, color = "red"
  ) + # Bike theft points
  labs(
    title = "Map of Bicycle Theft Locations in Toronto",
    x = "Longitude", y = "Latitude"
  ) +
  coord_sf(
    xlim = c(-79.6303856025883, -79.1180336515019),
    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
  ) +
  theme_minimal() +
  theme(
    panel.background = element_blank(), # Remove panel background
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank(), # Remove minor grid lines
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Save the plot
# ggsave(here("other/charts/bicycle_theft_heatmap.png"))
```

>>>>

```{r}
# Create a pie chart for the status of bicycle thefts
bike_thefts %>%
  count(STATUS) %>%
  ggplot(aes(x = "", y = n, fill = STATUS)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(title = "Bicycle Theft Status (Stolen vs Recovered)") +
  theme_minimal()
```

```{r}
# Create a bar chart for bicycle thefts by day of the week
bike_thefts %>%
  count(OCC_DOW) %>%
  ggplot(aes(x = reorder(OCC_DOW, -n), y = n, fill = OCC_DOW)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Bicycle Thefts by Day of the Week", x = "Day of the Week", y = "Number of Thefts") +
  theme_minimal()
```

@@

# Plot the map with bike theft locations data
ggplot() +
  geom_sf(data = streets, color = "gray", size = 0.3, alpha = 0.6) + # OSM street map layer
  geom_point(
    data = coordinates_data, aes(x = longitude, y = latitude),
    size = 0.5, color = "red"
  ) + # Bike theft points
  labs(
    title = "Map of Bicycle Theft Locations in Toronto",
    x = "Longitude", y = "Latitude"
  ) +
  coord_sf(
    xlim = c(-79.6303856025883, -79.1180336515019),
    ylim = c(43.5822069220627, 43.8554571861712), expand = FALSE
  ) +
  theme_minimal() +
  theme(
    panel.background = element_blank(), # Remove panel background
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank(), # Remove minor grid lines
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```
